### 2023-04-24 Article.Rmd
1

affiliation:
  - id            : "1"
    institution   : "Ovidius University, Constanța"
  - id            : "2"
    institution   : "Bucharest University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

@@

## Literature review

In the past few years, social media has risen to become a significant means of communication between public institutions and citizens. This has paved the way for increased citizen engagement in the decision-making process, which is considered essential for fostering trust and enhancing accountability. This literature review delves into the significance of citizen involvement in the communication process of public institutions via social media. It does so by amalgamating and synthesizing the findings of diverse studies, each focusing on various facets of social media and citizen engagement within the European Union.

>>>>

affiliation:
  - id            : "1"
    institution   : "Ovidius University, Constanța - Faculty of Law and Administrative Sciences"
  - id            : "2"
    institution   : "Bucharest University"

authornote: |
  Department of Administrative and Social Sciences

@@

## Literature review
In the past few years, social media has risen to become a significant means of communication between public institutions and citizens. This has paved the way for increased citizen engagement in the decision-making process, which is considered essential for fostering trust and enhancing accountability. This literature review delves into the significance of citizen involvement in the communication process of public institutions via social media. It does so by amalgamating and synthesizing the findings of diverse studies, each focusing on various facets of social media and citizen engagement within the European Union.
